COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2020-06-20 main.tex
Fix up figures, add simulated ALMA stuff

@@

@@

>>>>

Text width: \the\textwidth

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{alma/skymodel_e2m2.png}
    \includegraphics[width=0.5\textwidth]{alma/xy_e2m2.png}
    \caption{Simulated ALMA observations.  Top. The skymodel based on the radial collision distribution from the e2m2 simulation. The size of the disk has been scaled by a factor of 10 and placed at 100 pc. Middle. The cleaned image using combined observations in configurations 8, 9, and 10. The 3:1 and 2:1 resonance dust gaps are visible. \label{fig:alma_sim_obs}}
\end{center}
\end{figure}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/alma_profiles}
    \caption{Caption goes here.\label{fig:alma_profiles}}
\end{figure*}

@@

\section{Appendix: Nonaxisymmetric Structure in Boley 2017}\label{sec:boley_plot}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/boley_rtheta}
    \caption{Caption goes here\label{fig:boley_rtheta}}
\end{figure*}
